---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# BIDSconvertR

<!-- badges: start -->

[![DOI](https://zenodo.org/badge/195199025.svg)](https://zenodo.org/badge/latestdoi/195199025)

```{r, include = FALSE}
hexSticker::sticker("inst/figure/mri.png", package = "BIDSconvertR", 
                    p_size = 18, s_x = 1, s_y = .75, s_width =.5, 
                    h_color = "blue", h_fill = "darkgreen", 
                    filename = "inst/figure/BIDSconvertR.png")
```


The hexagonal sticker is based on the MRI svg graphics provided by : 

[MRI icons on flaticon]("https://www.flaticon.com/free-icons/mri")
Mri icons created by mavadee - Flaticon</a>


<!-- badges: end -->

The goal of BIDSconvertR is to ...

## Installation

You need the R package 'devtools' to install packages from Github

```{r}
install.packages("devtools")
```

Now you are able to install the development version of BIDSconvertR.

```{r}
devtools::install_github(repo = "wulms/bidsconvertr")
```

Please install also the following package.

```{r}
devtools::install_github("muschellij2/papayaWidget")
```



## Usage


Please install your needed version of dcm2nii using:

```{r}
install_dcm2niix("v1.0.20211006")
```


## Citation







