---
params:
  study: "StudyInfo"
  converter_path: "converter_path"
title: "`r params$study`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: simplex
---

<style>                     
.navbar {
  background-color:black;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    background-color: grey;
    color: white;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: grey;
}
.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: red;
}
.navbar-inverse .navbar-collapse,
.navbar-inverse .navbar-form {
  border-color: green;
}
.navbar-brand {
color:white!important;
}
.nav-tabs-custom .nav-tabs li.active a {
  color: blue;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
  color: black;
}
}
</style>  

```{r setup, include=FALSE}
# library(patchwork)
library(bidsconvertr)
```

```{r include=FALSE}
# debug
# converter_path = "C:/Science/bidirect_bids_test/bids_bidirect_converter/"
# bids_path <- paste0(converter_path, "/bids/sourcedata")
# json_metadata <- paste0(converter_path, "/json_metadata.tsv")
# sequence_map <- paste0(converter_path, "/sequence_map.tsv")

# original
bids_path <- paste0(params$converter_path, "/bids/sourcedata")
json_metadata <- paste0(params$converter_path, "/json_metadata.tsv")
sequence_map <- paste0(params$converter_path, "/sequence_map.tsv")

# create paths
dataset_description <- paste0(bids_path, "/dataset_description.json")
dataset_readme <- paste0(bids_path, "/README")
dataset_changes <- paste0(bids_path, "/CHANGES")



# read files

bids_readme <- read_lines(dataset_readme, skip_empty_rows = FALSE, lazy = FALSE) %>% paste(., collapse = "  \n  ")
bids_changes <- read_lines(dataset_changes, skip_empty_rows = FALSE, lazy = FALSE) %>% paste(., collapse = "  \n  ")

metadata_dataset <- fromJSON(file = dataset_description)


sequence_map_df <- read_tsv(sequence_map, show_col_types = FALSE, lazy = FALSE)
  
json_df <- read_tsv(json_metadata, show_col_types = FALSE, lazy = FALSE) %>% 
  mutate(PatientSex = as.character(PatientSex))

json_merged_df <- json_df %>% 
  left_join(sequence_map_df) %>%
  relocate(subject, group, session, sequence, BIDS_type, BIDS_sequence, relevant) %>%
  select(-total, -possible_sequence)

```


<!-- Debug -->
<!-- ============================================ -->

<!-- Part1 -->
<!-- ----------------- -->

<!-- ```{r} -->
<!-- bids_path -->
<!-- dataset_description -->
<!-- dataset_readme -->
<!-- dataset_changes -->
<!-- json_metadata -->
<!-- bids_readme -->
<!-- bids_changes -->
<!-- metadata_dataset -->

<!-- ``` -->

<!-- Part2 -->
<!-- ---------------------- -->

<!-- ```{r} -->
<!-- json_merged_df -->

<!-- ``` -->


Summary
===========================================================================

Raw infos {data-width=170}
--------------------------------------------------------------------------

### Overview

#### Subjects 
`r  json_merged_df %>% select(subject) %>% unique() %>% count() %>% kable()`
#### Sessions
`r  json_merged_df %>% select(session) %>% count()  %>% kable()` 
#### Sequences
`r  json_merged_df %>% select(relevant) %>% count()  %>% kable()`
#### Relevant
`r  json_merged_df %>% filter(relevant == 1) %>% select(sequence) %>% count()  %>% kable()`  
#### Irrelevant
`r  json_merged_df %>% filter(relevant == 0) %>% select(sequence) %>% count()  %>% kable()`
#### Scanner information
`r  json_merged_df %>% select(ManufacturersModelName) %>% count()  %>% kable()`  
`r  json_merged_df %>% select(Modality) %>%  count()   %>% kable()`  
`r  json_merged_df %>% select(MagneticFieldStrength) %>%  count()   %>% kable()` 
`r  json_merged_df %>% select(DeviceSerialNumber) %>%  count()   %>% kable()`  
`r  json_merged_df %>% select(SoftwareVersions) %>%  count()   %>% kable()`  
`r  json_merged_df %>% select(StationName) %>%  count() %>% kable()` 
`r  json_merged_df %>% select(InstitutionalDepartmentName) %>%  count()  %>% kable()`  
`r  json_merged_df %>% select(InstitutionName) %>%  count()  %>% kable()`  
 




Study Summary {data-width=750}
-----------------------------------------------------------------------

### Dataset Information

__Authors:__ `r metadata_dataset$Authors`  
__Funding:__ `r metadata_dataset$Funding`  
__How to acknowledge:__ `r metadata_dataset$HowToAcknowledge`  
__License__: `r metadata_dataset$License`  
__References and Links:__   
`r metadata_dataset$ReferencesAndLinks  %>% paste(., collapse = "  \n  ")`  
__BIDS Version:__ `r metadata_dataset$BIDSVersion`  

__README__ 

```{r}
cat(bids_readme)
```

__Changes__

```{r}
cat(bids_changes)
```




Sequences 
=======================================================================

Column {data-width=550}
-----------------------------------------------------------------------

### Chart A

```{r fig.width = 7, fig.height = 7}
json_merged_df %>% 
    df_select_n() %>% 
  plot_bar()



```

Column {data-width=350}
-----------------------------------------------------------------------

### Relevant sequences

```{r}
json_merged_df %>% 
  df_select_n() %>%
  filter(relevant == 1) %>% select(-relevant) %>%
  spread(. ,session, value = freq) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>% 
 scroll_box(height = "400px")
```

### Irrelevant sequences

```{r}
json_merged_df %>% 
  df_select_n() %>%
  filter(relevant == 0) %>% select(-relevant) %>%
  spread(. ,session, value = freq)  %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>% 
 scroll_box(height = "400px")
```


Group-summary
=================================================================

Column {data-width=700}
---------------------------------------------
### Group plot

```{r fig.width = 10, fig.height = 8}
p <-json_merged_df %>%
      df_select_n_group() %>% 
      ggplot(aes(x = session, y = freq, fill = PatientSex)) + 
      geom_bar(position="stack", stat = "identity") + 
      theme_minimal() +
      facet_wrap(BIDS_type ~ BIDS_sequence + group, nrow = 2, labeller = label_both) +
    ggtitle("Barplots of n=Sequence , split by session-id and group-id") 


p
```

Column {data-widht=300}
--------------------------------------------------

### Group table

```{r}
json_merged_df %>% 
    df_select_n_group() %>% 
  select(-relevant) %>%
  spread(session, freq)  %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>% 
 scroll_box(height = "800px")
```


Subjects-summary
==============================================================

Column {data-width=1000}
---------------------------------------------------------------

### All
```{r}

sessions <- json_merged_df$session %>% n_distinct()

json_merged_df  %>%
   calculate_comp_subjects(., sessions = sessions)  %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(height = "800px")


```

```{r}
```



JSON Metadata
=================================================================

Column {data-width=1000}
-----------------------

### JSON Metadata

```{r}
json_merged_df   %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(width = "1800px", height = "800px") 


```


Age-distribution
========================================================================

Column {data-width=500}
--------------------------------------------------

### Boxplots

```{r fig.width=11, fig.height = 8}
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")


p_age <-json_merged_df %>%
  df_select_patient_info() %>%
  ggplot(aes(x = session, y = Age)) +
  geom_boxplot() +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                   trim = TRUE, 
                   alpha = .5, 
                   adjust = .8, 
                   scale = "width") +
  geom_point() +
  facet_wrap(. ~ group, labeller = label_both, nrow = 1) +
  ggtitle("Boxplots of Age, split by session-id and group-id")

p_agesex <- json_merged_df %>%
  df_select_patient_info() %>%
  ggplot(aes(x = session, y = Age)) +
  geom_boxplot() +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                   trim = TRUE, 
                   alpha = .5, 
                   adjust = .8, 
                   scale = "width") +
  geom_point() +
  facet_wrap(. ~ group + PatientSex, labeller = label_both, nrow = 1) +
  theme(legend.position = "bottom") +
  ggtitle("Boxplots of Age and Sex, split by session-id and group-id") 

p_age / p_agesex
```

Column {data-width=500}
--------------------------------------------------

### Statistics

```{r}
json_merged_df %>%
  df_select_patient_info() %>%
  group_by(session, group) %>%
  dplyr::summarize(mean = mean(Age),
            median = median(Age),
            sd = sd(Age),
            var = var(Age),
            iqr = IQR(Age),
            n = n()) %>%
  mutate(across(where(is.numeric), round, digits = 2)) %>%
  select(session, n, everything())  %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(height = "800px")
```



Metadata {data-navmenu="QC"}
===========================================================================

These tables could indicate implausibilities (like errors in ID), based on entrys, that contain sensitive information on the subject.  

Column {data.width = 500}
--------------------------------------------------------

### ID changes - Shapeshifters

```{r}
clean_string <- function(input, pattern) {
  input %>%
    str_remove_all(pattern) %>%
    str_remove_all("[:punct:]+")
}



json_merged_df %>%
  select(session, subject, PatientID, PatientName) %>%
  mutate(
    subject = str_remove(subject, "sub-"),
    PatientID = clean_string(PatientID, json_merged_df$subject),
    PatientName = clean_string(PatientName, json_merged_df$subject)
  ) %>%
  filter(PatientID != "" | PatientName != "") %>%
  unique() %>%
  datatable_setting()
```

### Birthdata changes - Reincarnated

```{r}
json_merged_df %>%
  select(subject, PatientBirthDate) %>%
  unique() %>%
  select(subject) %>%
  count() %>% 
  filter(freq > 1) %>%
  left_join(json_merged_df) %>%
  select(subject, session, AcquisitionDateTime, PatientBirthDate) %>%
  mutate(AcquisitionDateTime = as.Date(AcquisitionDateTime)) %>%
  unique() %>%
  group_by(subject) %>%
  mutate(
    Age = difftime(AcquisitionDateTime, PatientBirthDate) %>% time_length("years") %>% round(1),
    BirthDateDiff = difftime(PatientBirthDate, lag(PatientBirthDate)) %>% time_length("years") %>% round(1)
  ) %>%
  datatable_setting()

```

Column {data.width = 500}
-----------------------------------------------------------

### Sex changes - Clownfishes

```{r}
json_merged_df %>%
  select(subject, PatientSex) %>%
  unique() %>%
  select(subject) %>%
  count() %>% 
  filter(freq > 1) %>%
  left_join(json_merged_df) %>%
  select(subject, session, PatientSex) %>% unique() %>%
  datatable_setting()
      
    
  
```

### Two acquisition dates at same session id - Time travellers

```{r}
json_merged_df %>%
  select(subject, session, AcquisitionDateTime) %>%
  mutate(AcquisitionDateTime = as.Date(AcquisitionDateTime)) %>%
  unique() %>%
  group_by(subject) %>%
  select(session) %>%
  count() %>% 
  filter(freq > 1) %>%
  datatable_setting()
```


Sequence selection  {data-navmenu="QC"}
===========================================================================

```{r}
json_merged_df %>%
  select(BIDS_type, relevant, sequence, SeriesDescription, ProtocolName) %>%
  group_by(across(everything())) %>% 
  count() %>%
  select(BIDS_type, relevant, freq, everything()) %>%
  datatable_setting()


```

Duplicates  {data-navmenu="QC"}
==========================================================================

```{r}
json_merged_df %>%
  select(subject, session, sequence) %>% 
  group_by(across(everything())) %>% 
  count() %>% 
  filter(freq > 1) %>%
  left_join(json_merged_df) %>% 
  select(subject, session, sequence, Path) %>% 
  unique() %>%
  datatable_setting()
```

Parameters - anat {data-navmenu="QC"}
===================================================================================

```{r}
df_out <- json_merged_df %>%
  filter(BIDS_type == "anat") %>%
  filter(relevant == "1")

if(nrow(df_out) != 0){
  df_out %>%
  mutate(BIDS_sequence = as.factor(BIDS_sequence)) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(height = "800px")
} else {
  print("No anatomical files found.")
}
  
```

Parameters - dwi {data-navmenu="QC"}
===================================================================================

```{r}
df_out <-json_merged_df %>%
  filter(BIDS_type == "dwi") %>%
  filter(relevant == "1")

if(nrow(df_out) != 0){
  df_out %>%
  mutate(BIDS_sequence = as.factor(BIDS_sequence)) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(height = "800px")
} else {
  print("No diffusion-weighted files found.")
}
  
```

Parameters - func {data-navmenu="QC"}
===================================================================================

```{r}
df_out <-json_merged_df %>%
  filter(BIDS_type == "func") %>%
  filter(relevant == "1")

if(nrow(df_out) != 0){
  df_out %>%
  mutate(BIDS_sequence = as.factor(BIDS_sequence)) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling("striped") %>%
 scroll_box(height = "800px")
} else {
  print("No functional files found.")
}

 
  
```
